Pricing Parisian options under a Gaussian process

### 2017-04-28 paper(EN).tex
20170428

\vfill % Fill the rest of the page with whitespace
\end{titlepage}
\newpage
%\begin{abstract}
This study extends the Parisian option pricing model to general Gaussian processes to adapt more asset pricing model assumptions. This study uses a Wick-Ito integral to derive the consecutive and cumulative Parisian option pricing PDEs under Gaussian processes and construct an unconditionally stable implicit difference scheme. Additionally, a numerical method with efficient computation, namely, a chasing algorithm, is used to solve the pricing problem. When analysing the example of the price of consecutive and cumulative Parisian options under any Gaussian process, because the counter is not zero, the cumulative Parisian option is more likely a knock-out option, and the price is lower than that of the consecutive Parisian option. The variables that affect the prices of the Parisian option under a Gaussian process are a slow-growing variance function, smaller volatility, more likely profit and loss forecasts, steeper graph of the price of the Parisian option, and higher peak value.

{\bf Key Words: }Parisian Option, Gaussian Process, Chasing Algorithm, Brownian Motion, Implicit Difference Equations
%\end{abstract}

@@

Mixed fractional Brownian motion is a linear combination of standard Brownian motion and fractional Brownian motion. Suppose$B_t$ is a Brownian motion and $B_t^H$ is a fractional Brownian motion; then, $W_t=\alpha B_t+\beta B_t^H$, where $\alpha,\beta \in R$ and its covariance function is  $F(t,s)=\alpha^2(t\wedge s)+\beta(t^{2H}+s^{2H}-|t-s|^{2H})/2$ 
%We express $F(t,t)=F_t$，$dF_t/dt=U_t$ and provide a summary of each motion in Table \ref{tabl1}：
\begin{table}[htbp]
\centering
\caption{各种高斯过程的协方差函数}
\label{tabl1}
\begin{tabular}{ccc}
\hline
高斯过程& $F_t$ & $U_t$ \\
\hline
布朗运动 & $t$ & $1$ \\
分数布朗运动 & $t^{2H}$ & $2Ht^{2H-1}$ \\
双分数布朗运动 & $t^{2HK}$ & $2HKt^{2HK-1}$ \\
次分数布朗运动 & $(2-2^{2H-1})t^{2H}$ & $(4-2^{2H})Ht^{2H-1}$ \\
混合分数布朗运动 & $\alpha^2t+\beta^2t^{2H}$ & $\alpha^2+2H\beta^2t^{2H-1}$ \\
\hline
\end{tabular}
\end{table}

>>>>

\vfill % Fill the rest of the page with whitespace
\end{titlepage}
\newpage
\begin{abstract}
This study extends the Parisian option pricing model to general Gaussian processes to adapt more asset pricing model assumptions. This study uses a Wick-Ito integral to derive the consecutive and cumulative Parisian option pricing PDEs under Gaussian processes and construct an unconditionally stable implicit difference scheme. Additionally, a numerical method with efficient computation, namely, a chasing algorithm, is used to solve the pricing problem. When analysing the example of the price of consecutive and cumulative Parisian options under any Gaussian process, because the counter is not zero, the cumulative Parisian option is more likely a knock-out option, and the price is lower than that of the consecutive Parisian option. The variables that affect the prices of the Parisian option under a Gaussian process are a slow-growing variance function, smaller volatility, more likely profit and loss forecasts, steeper graph of the price of the Parisian option, and higher peak value.

{\bf Key Words: }Parisian Option, Gaussian Process, Chasing Algorithm, Brownian Motion, Implicit Difference Equations
\end{abstract}

@@

Mixed fractional Brownian motion is a linear combination of standard Brownian motion and fractional Brownian motion. Suppose$B_t$ is a Brownian motion and $B_t^H$ is a fractional Brownian motion; then, $W_t=\alpha B_t+\beta B_t^H$, where $\alpha,\beta \in R$ and its covariance function is  $F(t,s)=\alpha^2(t\wedge s)+\beta(t^{2H}+s^{2H}-|t-s|^{2H})/2$ 
We express $F(t,t)=F_t$，$dF_t/dt=U_t$ and provide a summary of each motion in Table \ref{tabl1}：

\begin{table}[htbp]
\centering
\caption{各种高斯过程的协方差函数}
\label{tabl1}
\begin{tabular}{ccc}
\hline
高斯过程& $F_t$ & $U_t$ \\
\hline
布朗运动 & $t$ & $1$ \\
分数布朗运动 & $t^{2H}$ & $2Ht^{2H-1}$ \\
双分数布朗运动 & $t^{2HK}$ & $2HKt^{2HK-1}$ \\
次分数布朗运动 & $(2-2^{2H-1})t^{2H}$ & $(4-2^{2H})Ht^{2H-1}$ \\
混合分数布朗运动 & $\alpha^2t+\beta^2t^{2H}$ & $\alpha^2+2H\beta^2t^{2H-1}$ \\
\hline
\end{tabular}
\end{table}
